Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-25 paper/sections/proof-reconstruction.tex
10:49pm 25/09/2017

\begin{equation}
\label{eq:split-definition}
% \mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) ∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))  & \text{if }φ ≡ φ₁ ∧ φ₂,\\
      &\\[2.5mm]

\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]

@@

\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]

\unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2.5mm]

@@

First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and in a similar way with disjunctions,
we define $rdisj$ function, to convert a general disjunction to a be right-associative disjunction.

@@

@@

>>>>

\begin{equation}
\label{eq:split-definition}
% \mysplit(φ) =
\begin{cases}
\unshunt(\mysplit(φ₁)) ∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))  & \text{if }φ ≡ φ₁ ∧ φ₂,\\
      &\\[2.5mm]
\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]

@@

\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]
\unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2.5mm]

@@

For the rest of inference rules, we need some transformations useful
to deal with conjunctions and disjunctions.

First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and following
a similar approach we define $rdisj$ function for disjunctions.

@@

The following function, buildOr intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a disjunctions, no other propositional shape we treat.
This approach for rearrangement is inspired on the treatment for nested
disjunctions in \citeauthor{bohme2010}~\cite{bohme2010}.

@@

\subsubsection{Reordering}
...
